Plots for Latent Hawkes Paper

### 2020-07-16 output_scripts/Paper_Plots.Rmd
try other cohort and try extend timeout limit to see if that fixes it

This is using the correct form of the compensator for a Hawkes process.

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 1

@@

Not completed. This would need the rankings to be
rerun for all cohorts.

@@

Here is where I need to be a bit more careful about using the correct fits.
Currently using all from Jing's saved output.

In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.

@@

current_cohort <- 1

@@

# ------------------- period
training_end <- nrow(df[df$day<=18,])
testing_end <- 1076
newx <- c(training_end:testing_end)

@@

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,200))
for(s in 1:200){
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
    predict.sim = m3_predict_sim[5:8,s],
    history.df = glick.df[1:training_end,])
  history_matrix <- temp_gl$history[,,1]

>>>>

<!-- This is using the correct form of the compensator for a Hawkes process. -->

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5

@@

<!-- Not completed. This would need the rankings to be -->
<!-- rerun for all cohorts. -->

@@

<!-- Here is where I need to be a bit more careful about using the correct fits. -->
<!-- Currently using all from Jing's saved output. -->

<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->

@@

current_cohort <- 3

@@

# ------------------- period
training_end <- nrow(df[df$day<=18,])
testing_end <- nrow(df)#1077 #929 for cohort 5
newx <- c(training_end:testing_end)

@@

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
for(s in 1:100){
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
    predict.sim = m3_predict_sim[5:8,s],
    history.df = glick.df[1:training_end,])
  history_matrix <- temp_gl$history[,,1]
